Generalization Errors of Hard Parameter Sharing: High-dimensional Asymptotics and Implications

### 2020-10-02 arxiv/examples.tex
revise

\begin{corollary}[Derived from Theorem \ref{thm_main_RMT}]\label{cor_MTL_loss}
	In the setting described above, assume further that a) the sample size $n_2$ of task two is greater than $(1 + \tau) p$, and b) there exists a small constant $c_0>0$ such that the signal-to-noise ratios satisfy 
	\be\label{choiceofpara0}
		p^{ c_0} \le \frac{p\kappa^2}{\sigma^2 }  \le p^{1-c_0},\quad  \frac{pd^2}{\sigma^2}=\OO(1).
	\ee
	%Let $B, A_1, A_2$ be the global minimum of equation \eqref{eq_mtl}. Then
	The prediction loss of the hard parameter sharing estimator for task two satisfies that
	\begin{align}\label{cor_MTL_error}
	%-\left[1- \left( 1-\frac{1}{\sqrt{\rho_1}}\right)^4\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2)  \le 
	 & \left|L(\hat{\beta}_2^{\MTL}) -\frac{\sigma^2}{\rho_1+\rho_2-1} - pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}\right|  \le  \left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2 ),
	 \end{align}
	 for any constant $c\in (0,c_0)$.
\end{corollary}

>>>>

\begin{corollary}[Derived from Theorem \ref{thm_main_RMT}]\label{cor_MTL_loss}
	In the setting described above, assume further that a) the sample sizes $n_1$ and $n_2$ are greater than $(1 + \tau) p$, b) $\Sigma_1=\Sigma_2=\id_p$, and c) %there exists a small constant $c_0>0$ such that 
	the signal and noise variances satisfy 
%	\be\label{choiceofpara0}
%	p^{-1/2+c_0}\sigma^2 + p^{c_0}d^2\le \kappa^2\le p^{1-c_0} (\sigma^2 +d^2)  .  	\ee
	\be\label{choiceofpara0}
	\sigma^2 \lesssim  \kappa^2   ,\quad  d^2 \ll {\kappa^2}.
	\ee
	%Let $B, A_1, A_2$ be the global minimum of equation \eqref{eq_mtl}. Then
	The prediction loss of the hard parameter sharing estimator for task two satisfies that
	\begin{align}\label{cor_MTL_error}
	%-\left[1- \left( 1-\frac{1}{\sqrt{\rho_1}}\right)^4\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2)  \le 
	  \left|L(\hat{\beta}_2^{\MTL}) -\frac{\sigma^2}{\rho_1+\rho_2-1} - pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}\right|  \le & \left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \\
	& +Cp \left[p^{-c_\varphi}(\sigma^2 +d^2)+p^{-c_\infty}\kappa^2 + d^4/\kappa^2\right],\nonumber
	 \end{align}
	 for a large constant $C>0$.
\end{corollary}
